\documentclass[9pt]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{url}
\usepackage{multicol}
\usepackage{multirow}
\usepackage[usenames, dvipsnames]{xcolor}
\usepackage{nopageno}
\usepackage{hyperref}

% just having fun ;)
\usepackage{fontawesome}
\usepackage{coloremoji}

\renewcommand{\arraystretch}{1.5}
\leftmargin=0.25in
\oddsidemargin=0.25in
\textwidth=6.0in
\topmargin=-1.2in
\textheight=10.00in

\raggedright
\pagestyle{empty}
%\pagenumbering{arabic}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

\newenvironment{changemargin}[2]{%
  \begin{list}{}{%
      \setlength{\topsep}{0pt}%
    \setlength{\leftmargin}{#1}%
    \setlength{\rightmargin}{#2}%
    \setlength{\listparindent}{\parindent}%
  \setlength{\itemindent}{\parindent}%
    \setlength{\parsep}{\parskip}%
    }%
  \item[]}{\end{list}
    }

\newcommand{\lineover}{
  \begin{changemargin}{-0.05in}{-0.10in}
    \vspace*{-9pt}
    \hrulefill \\
    \vspace*{-2pt}
  \end{changemargin}
}

\newcommand{\header}[1]{
  \begin{changemargin}{-0.5in}{-0.5in}
    \scshape{#1}\\
        \lineover
  \end{changemargin}
}

\newcommand{\name}[1]{
  %\begin{changemargin}{0.0in}{0.0in}
  %\begin{center}
  {\LARGE \scshape {#1}}
  %\end{center}
  %\lineover
  %\end{changemargin}
}

\newcommand{\contact}[4]{
  \begin{changemargin}{-0.65in}{-0.65in}
    \begin{multicols}{2}
      \name{{#1}}\vfill\null % this is name
                        \columnbreak
                        {#2}\\	
                        {#3}\\ 
                        {#4}\\ 
    \end{multicols}
  \end{changemargin}
}

\newenvironment{body} {
  \vspace*{-16pt}
        \begin{changemargin}{-0.6in}{-0.65in}
        }	
        {\end{changemargin}
}	


% END RESUME DEFINITIONS

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Name
\contact{Saurav Shekhar}
{{\hspace{172pt}}\faMobile (+41) 76 410 31 18}
{{\hspace{121pt}} \faEnvelope \href{mailto:sauravshekhar01@gmail.com}{sauravshekhar01@gmail.com}}
%{\hspace{190pt}Github: \href{http://github.com/sshekh}{\emph{{\textit{sshekh}}}}}
{{\hspace{177pt}} \faGithub \href{https://sshekh.github.io/}{sshekh.github.io}}  

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Education
\header{Education}
\vspace{4pt}
  \renewcommand{\arraystretch}{1}
  \begin{tabular}{rll}
    2016-2019 & \textbf{MSc Computer Science},  ETH Z{\"u}rich  & 5.52/6.0 \\
            & ESOP scholar, awarded to 3 admits among 150 in MSc Computer Science 2016 &\\
            & Thesis: \emph{Adaptive Step Size in Boosting Black Box Variational Inference} &\\\\
    2012-2016 & \textbf{B.Tech Computer Science},  Indian Institute of Technology, Kanpur & 9.1/10 \\ 
            &  Academic Excellence Award for year 2012-13 & \\\\
  \end{tabular}

\header{Publications}
Gideon Dresdner, {\bf Saurav Shekhar},  Fabian Pedregosa, Francesco Locatello,  Gunnar Rätsch. From Global to Local Boosting Variational Inference, \textit{International Conference on Machine Learning (ICML)}, 2020 ({\bf under review}) \\

\vspace{2mm}
Kim Albertsson, Sergei Gleyzer, Marc Huwiler, Vladimir Ilievski, Lorenzo Moneta, {\bf Saurav Shekhar}, Victor Estrade, Akshay Vashistha, Stefan Wunsch and Omar Andres Zapata Mesa. New Machine Learning Developments in ROOT/TMVA, \textit{23rd International Conference on Computing in High Energy and Nuclear Physics (CHEP 2018)}, September 2019.
\href{https://doi.org/10.1051/epjconf/201921406014}{doi.org/10.1051/epjconf/201921406014}

\vspace{3mm}
\header{Professional experience}
\begin{body}
  \vspace{14pt}
 
  \begin{description}
    \item[\normalsize{Google Z{\"u}rich}] \hfill {Nov '19 - present} \\
      \textit{Software Engineer, YouTube trust and safety} \hfill \textit{Z{\"u}rich} \\
      \begin{itemize}
      \item Developing machine learning solutions for detecting and taking down abusive video content at YouTube
      \end{itemize}
  \end{description}

  \begin{description}
    \item[Google Research] \hfill {June '18 - Sep '18} \\
    \textit{Software Engineering Intern, Handwriting Recognition} \hfill \textit{Mountain View}\\
  \normalsize{Zero shot emoji recognizer}  🌎
  \begin{itemize}
    \item Researched Machine Learning models for learning better embeddings for emoji recognition
    %\item (detail): Aim of the project is to design ML models that can classify handwriting strokes into different emoji classes using just emoji images during training.
    % Experimented with image based models by rendering stroke data to image and training Similarity Networks for zero shot learning.
    % Achieved 40\% top-25 accuracy on 1.6k emoji classes
  \end{itemize}
 \end{description}

  \begin{description}
    \item[Amazon CoreAI] \hfill {Mar '18 - June '18} \\
      \textit{Software Engineering Intern} \hfill \textit{Berlin} \\
      \normalsize{Speeding up model evaluation for black box optimization}
      \begin{itemize}
        \item Trained ML models on thousands of hyperparameter configurations and created lookup tables with extrapolation for epochwise simulation of black box model.
        %\item (detail) Trained Machine Learning models on thousands on hyperparameter configurations generated with pseudo-grid sampling and collected the results for different dataset types. Created lookup tables with extrapolation for epochwise simulation of black box model on any given hyperparameter configuration.
        %Sped up evaluation of Hyperparameter Optimization algorithms by several orders of magnitude using offline tables
      \end{itemize}

    \item[Goldman Sachs] \hfill {May '15 - July '15} \\
      \textit{Summer internship, FICC}  \hfill \textit{Bangalore} \\
      \normalsize{Real-time Market Data Monitor}
      \begin{itemize}
        \item Implemented monitoring and alerting for latency spikes and various market data sanity checks and improved market data subscription
          %\item Technology Used: Java, JNI, Bash, Reuters RFA API
      \end{itemize}

  \end{description}

\end{body}

%\vspace{5 mm}
\header{Projects}
%\vspace{2 mm}
\begin{body}
  \vspace{14pt}

  \begin{description}
    \item[\normalsize{Dialogue generation using Seq2seq models}] \hfill \textit{April '17 - June '17} \\
      \textit{Course project in Natural Language Understanding under Prof. Thomas Hofmann}
      \begin{itemize}
        \item Starting with a basic sequence to sequence model for conversational
          agent, improved upon the baseline using attention models, stacked RNNs,
          mutual information (for diversifying output) and beam search.
        \item Introduced histograms of word frequency as a metric to evaluate 
          model performance (especially diversity) along with perplexity and BLEU 
          score.
      \end{itemize}

    \item[\normalsize{Twitter Sentiment Classification}] \hfill \textit{March '17 - July '17} \\
      \textit{Course project (Kaggle challenge) in Computational Intelligence Lab
      under Prof. Thomas Hofmann}
      \begin{itemize}
        \item Used GloVe and Word2Vec to extract word embeddings from tweets, 
          along with a combination of unsupervised sentence level embeddings to
          form feature vectors.
        \item Used an ensemble of LSTM, GRU and Convolutional Networks
          to achieve a classification accuracy of 89\% on a dataset of 2.5 million
          tweets. This was the {\bf top} scoring model on the leaderboard. 
      \end{itemize}

    \item[\normalsize{Random Graphs}]	\hfill 	\textit{July '15 - Nov '15} \\
      \textit{Undergraduate project under Prof. Surender Baswana, IIT Kanpur} 
      \hfill \href{https:sshekh.github.io/www/cs498a/report.pdf}{\textit{\textcolor{ProcessBlue}{link to report}}}
    \begin{itemize}
      \item Studied Erdos-Renyi phase transitions and expected linear time 
        algorithms for finding biconnected components in Random graphs.
      \item Worked on average case analysis of an incremental algorithm for 
        maintaining DFS tree in an undirected graph.
    \end{itemize}

    \item[\normalsize{Optimized implementation of Latent Dirichlet Allocation}]  \hfill \textit{March '17 - June '17} \\
      \textit{Course project in How to Write Fast Numerical Code under Prof. Markus P{\"u}schel}
      \begin{itemize}
        \item Enhanced the performance of a standard Latent Dirichlet Allocation (LDA)
          implementation on single core using memory usage improvements, use of 
          SIMD instructions, cache analysis etc.
        \item Achieved a speedup of 11x over original C implementation written by authors
          of LDA.
      \end{itemize}

    \item[\normalsize{Robust PCA via Convex Optimization}] \hfill \textit{Apr '16} \\
      \textit{Term paper in Convex Optimization under Prof. Ketan Rajawat, IIT Kanpur}
      \begin{itemize}
      \item Studied and compared the current best algorithms for low rank matrix recovery like the 
        accelerated proximal
        gradient algorithm (APG), Augmented Lagrange Multiplier method (ALM), Dual method etc.
      \item Ran simulations with different size and error matrix and compared results of all algorithms 
        on different metrices 
          like time taken, reconstruction error, error-rate with iterations etc.
      \end{itemize}

    %	  \item[\normalsize{Concurrent data Structures in Haskell}] \hfill  \textit{July '15 - Nov '15} \\
    %	  \textit{Course project in Functional Programming under Prof. Piyush Kurur, IIT Kanpur}
    %	  \begin{itemize}
    %	   % \item Aim was to develop a non-blocking queue data structure in Haskell 
    %	   \item Implemented Michael \& Scott's lock-free queue algorithm in Haskell.
    %	   \item Used atomic-primops package for CAS and other atomic operations.
    %	   \item Project developed as an open source Cabal Package.
    %	  \end{itemize}

  \item[\normalsize{Scala to MIPS Assembly Compiler}] \hfill \textit{Jan '15 - Apr '15} \\
    \textit{Course Project in Compilers under prof. Subhajit Roy, IIT Kanpur}
  \begin{itemize}
    \item Programmed a Scala to MIPS cross compiler with support for basic datatypes, conditional statements, looping statements, arrays, nested functions, recursion and object oriented features.
    \item Awarded as the $2^{nd}$ best project for the course out of 22 teams.
  \end{itemize}

\item[\normalsize{Extension of NACHOS}]  \hfill \textit{Aug '14 - Nov '14} \\
  \textit{Course Project in Operating Systems under prof. Mainak Chaudhuri, IIT Kanpur}
  \begin{itemize}
    \item Extended the standard system call library of NachOS and implemented Fork, Exec, Join, Yield, Sleep, Exit system calls.
      Implemented process scheduling algorithms like UNIX scheduling, FIFO, Round robin, SJF and non-preemptive scheduling.
    \item Programmed page replacement algorithms: Random allocation, FIFO, LRU and LRU-clock and evaluated relative performance.
  \end{itemize}

  \end{description}
  \smallskip
\end{body}

\vspace{2 mm}
\header{Academic}
\begin{body}
  \vspace{14pt}
        \begin{changemargin}{0.15in}{0.15in}
          \begin{itemize}
            \item Research Assistant, Biomedical Informatics Group, ETH Z{\"u}rich, summer 2019
            \item Research Assistant, Information Science and Engineering Group, ETH Z{\"u}rich, fall 2017
            \item Teaching Assistant, Data Structures and algorithms, IIT Kanpur, fall 2015
            \item Teaching Assistant, Advanced algorithms, IIT Kanpur, fall 2015
            \item Secured All India Rank 958 in IIT-JEE among 500,000 candidates.
            \item Selected in Top 1\% of each of the National Standard Examinations 
              in Physics (NSEP), Chemistry (NSEC) and Astronomy (NSEA) and Regional
              Mathematics Olympiad.
          \end{itemize}
        \end{changemargin}
\end{body}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Relevant Courses
% \vspace{3 mm}
% \header{Relevant Courses}
% 
% \vspace{3 mm}
% \begin{body}
% 	\vspace{4pt}
% 	\begin{changemargin}{0.15in}{0.15in}
% 	\begin{multicols}{3}
%         Operating Systems  \\
%         Principles of Programming languages \\
% 	Functional Programming \\
% 	Applied Stochastic Processes \\
% 	Probabilistic Machine Learning \\
% 	Convex Optimization \\
% 	Algorithms Lab $^{*}$ \\
% 	Machine Learning $^{*}$ \\
% 	Data Mining $^{*}$ \\
% 	Probabilistic AI $^{*}$ \\
% 	Advanced Systems lab $^{*}$
% 	\end{multicols}
% 	\end{changemargin}
% 	\footnotesize $^{*}$ Expected to be completed by Feb' 17
% \end{body}

\vspace{2 mm}
\header{Miscellanous}
%\vspace{2 mm}
\begin{body}
  \vspace{14pt}
        \begin{changemargin}{0.15in}{0.15in}
          \begin{itemize}
            \item Open source contributions: CERN root project, PyMC4, PyMC3 (minor)
            \item Google Hash Code 2017 onsite Finalist, under top $50$ worldwide 
              among 3000 teams in the qualification round.
            \item Ranked $10^{th}$ among 60 teams and awarded a bronze medal at 
              ACM ICPC SWERC 2016 Regionals.
            \item $6^{th}$ place among top 25 teams selected (among 8000 in online 
              rounds) for the Codechef Snackdown onsite finale 2015. \\
            \item Secretary, Programming Club (\textit{2013-2014}) - Assisted in
              organizing Programming competitions 
              and took introductory programming lecture for the freshers.
              %\item Worked with a team of 5 members on creating and testing the 
              %problems for IOPC, 
              %the annual 24 hr long algorithmic programming contest during 
              %	Techkriti 2015. 901 teams participated in the contest.
            %\item Advanced to Round 2 of Facebook Hackercup 2013 (position 287), and Round 2 of Google Code Jam 2014. \\
              %\item Secured position 11 and 20 among 6000 Indian participants in Codechef July 
              %challenge and June challenge 2014 respectively \\
            \item Secured $1^{st}$ place in IHPC, high performance computing contest at Techkriti 14. \\
              %\item Attended the large scale optimization for machine learning summer school, 2016 at IISC, Bangalore \\
              %\item Attended the mini symposium on Computation and Optimization held at IIT Kanpur \\
            \item \emph{\textbf{Languages:}} English (Full Professional fluency), 
              German (Intermediate), Hindi/Urdu (Native)
          \end{itemize}
        \end{changemargin}
\end{body}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Skills
\vspace{3 mm}
\header{Technical Skills}

\vspace{3 mm}
\begin{body}
  \vspace{14pt}
        \begin{changemargin}{0.15in}{0.15in}
          \emph{\textbf{Coursework:}} Computer Vision, Probabilistic Machine Learning,
          Graphical models for image analysis, Causality \emph{audited})
          Deep Learning, Natural Language Understanding, Machine 
          Learning, Hardware Architectures in Machine Learning, 
          How to Write Fast Numerical Code, Algorithms Lab, Applied Stochastic Processes \\
          \emph{\textbf{Programming Languages: }}{} C++ (Proficient), Python (Proficient), 
          Bash\\
          \emph{\textbf{Software: }}{} PyTorch, Tensorflow, Tensorflow Probability, Edward, CUDA (cuBLAS),
          SQL, Git, \LaTeX, PyMC, Pandas \\
        \end{changemargin}
\end{body}

\end{document}
